# Tables

(ref:table1Caption) Spatial and depth stratum allocation and completed set counts (blue) for the `r yr` Sablefish research and assessment survey.


```{r table1, echo=FALSE}

       Strata  <- c(paste( "S", "\\textsubscript{1}", " (South West Coast Vancouver Island or SWCVI)", sep=''),
                    paste( "S", "\\textsubscript{2}", " (North West Coast Vancouver Island or NWCVI)", sep=''),
                    paste( "S", "\\textsubscript{3}", " (Queen Charlotte Sound or QCS)", sep=''),                                     paste( "S", "\\textsubscript{4}", " (South West Coast Haida Gwaii or SWCHG)", sep=''),                            paste( "S", "\\textsubscript{5}", " (North West Coast Haida Gwaii or NWCHG)", sep=''),                                   "Total ")
       act.strata<- paste("select Year, DEPTH_STRATUM, SPATIAL_STRATUM, COUNT([SET]) AS sets ",
                           "from dbo.GFBIO_RESEARCH_TRIPS ",
                           "group by Year, DEPTH_STRATUM, SPATIAL_STRATUM ",
                           "having (Year = ", yr, " )", sep="")
       # surv.strata <- GetSQLData(act.strata,"Sablefish")
       # write.table(surv.strata, file = paste(path,"table1.csv", sep=''),
       # row.names=FALSE, na="", col.names=TRUE, sep=",")
       surv.strata <-  read.csv(paste(path,'table1.csv', sep=''), header=T)

       RD1      <- c(6,6,8,6,6,32)
       RD1fish  <- surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD1"]
       RD1fish[6]  <- sum(surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD1"])
       RD2fish  <- surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD2"]
       RD2fish[6]  <- sum(surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD2"])
       RD3fish  <- surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD3"]
       RD3fish[6]  <- sum(surv.strata$sets[surv.strata$DEPTH_STRATUM =="RD3"])     
       RD2      <- c(8,7,6,6,7,34)
       RD3      <- c(5,5,5,5,5,25)
       Total    <- c(19,18,19,17,18,91)
       Totfish  <- c(RD1fish[1]+RD2fish[1]+RD3fish[1], RD1fish[2]+RD2fish[2]+RD3fish[2],
                     RD1fish[3]+RD2fish[3]+RD3fish[3], RD1fish[4]+RD2fish[4]+RD3fish[4],
                     RD1fish[5]+RD2fish[5]+RD3fish[5], RD1fish[6]+RD2fish[6]+RD3fish[6]) # addition
       dataf    <- data.frame(Strata, RD1, RD1fish, RD2, RD2fish,RD3, RD3fish, Total, Totfish) 
       yrRD1    <- paste("RD", "\\textsubscript{1} ",yr, sep='') 
       yrRD2    <- paste("RD", "\\textsubscript{2} ",yr, sep='')
       yrRD3    <- paste("RD", "\\textsubscript{3} ",yr, sep='')
       yrTot    <- paste("Total ", yr, sep="")
       
       colnames(dataf) <- c("Spatial Strata", paste("RD", "\\textsubscript{1}", sep=''), yrRD1, 
                                              paste("RD", "\\textsubscript{2}", sep=''), yrRD2,
                                              paste("RD", "\\textsubscript{3}", sep=''), yrRD3,
                                              "Total", yrTot)
   
       kableExtra::kable(dataf, booktabs = TRUE,linesep = "",
                   format = "latex",
                   escape = F, # allows textsubscript latex
                   caption = "(ref:table1Caption)") %>%
              row_spec(0,    bold = T) %>%
              row_spec(5, hline_after = T) %>%
              column_spec(2, width  = "0.5cm") %>%
              column_spec(3, width  = "0.5cm", color="blue" ) %>%
              column_spec(4, width  = "0.5cm") %>%
              column_spec(5, width  = "0.5cm", color="blue") %>% 
              column_spec(6, width  = "0.5cm") %>% 
              column_spec(7, width  = "0.5cm", color="blue") %>%          
              column_spec(8, width  = "0.7cm") %>%
              column_spec(9, width  = "0.5cm", color="blue") %>% 
              row_spec(0, color="black") %>%
              row_spec(6, bold=T) %>%
              add_header_above(c(" "= 1, "Depth Strata" = 6, " " = 2), bold=T) %>%
       kableExtra::kable_styling(font_size = 9, position = "left",latex_options = "hold_position")
  
  
```
(ref:table2Caption) Target number of 25-trap camera survey sets and completed counts (blue) for the `r yr` Sablefish research and assessment survey.


```{r table2,  echo=FALSE}
    # run this query for numbers or refer to procedure exec dbo.Build_Seabird_tables 

    # SELECT SPATIAL_STRATUM, DEPTH_STRATUM, YEAR, COUNT(FE_MAJOR_LEVEL_ID) AS CountSets
    # FROM  (SELECT SENS.YEAR, SENS.TRIP_ID, SENS.FE_MAJOR_LEVEL_ID, SENS.SBE,  
    # SENS.ACC, SENS.CTD, SENS.CAM, SENS.DO, 
    # derivedtbl_1.DEPTH_STRATUM,     derivedtbl_1.SPATIAL_STRATUM
    # FROM  (SELECT  dbo.SURVEY_trips_vw.YEAR, FE.TRIP_ID, FE.FE_MAJOR_LEVEL_ID, FE.FE_MINOR_LEVEL_ID, 
    # CASE WHEN FE_EVENT_SENSOR_DESC LIKE '%sbe39%' THEN 1 ELSE 0 END AS SBE, 
    # CASE WHEN FE_EVENT_SENSOR_DESC LIKE '%accelerometer%' THEN 1 ELSE 0 END AS ACC, 
    # CASE WHEN FE_EVENT_SENSOR_DESC LIKE '%ctd%' THEN 1 ELSE 0 END AS CTD, 
    # CASE WHEN FE_EVENT_SENSOR_DESC LIKE '%camera%' THEN 1 ELSE 0 END AS CAM, 
    # CASE WHEN FE_EVENT_SENSOR_DESC LIKE '%oxygen%' THEN 1 ELSE 0 END AS DO
    # FROM  GFBioSQL.dbo.TRAP_SENSOR INNER JOIN
    # GFBioSQL.dbo.FE_EVENT_SENSOR ON GFBioSQL.dbo.TRAP_SENSOR.FE_EVENT_SENSOR_CODE = 
    # GFBioSQL.dbo.FE_EVENT_SENSOR.FE_EVENT_SENSOR_CODE INNER JOIN
    # GFBioSQL.dbo.FISHING_EVENT AS FE ON GFBioSQL.dbo.TRAP_SENSOR.FISHING_EVENT_ID = 
    # FE.FISHING_EVENT_ID INNER JOIN
    # dbo.SURVEY_trips_vw ON FE.TRIP_ID = dbo.SURVEY_trips_vw.TRIP_ID
    # GROUP BY FE.TRIP_ID, FE.FE_MAJOR_LEVEL_ID, FE.FE_MINOR_LEVEL_ID, dbo.SURVEY_trips_vw.YEAR, 
    # GFBioSQL.dbo.FE_EVENT_SENSOR.FE_EVENT_SENSOR_DESC
    # HAVING (dbo.SURVEY_trips_vw.YEAR = 2022)) AS SENS INNER JOIN
    # (SELECT Year, TRIP_ID, [SET], DEPTH_STRATUM, SPATIAL_STRATUM, SET_TYPE
    # FROM   dbo.GFBIO_RESEARCH_TRIPS) AS derivedtbl_1 ON SENS.TRIP_ID = 
    # derivedtbl_1.TRIP_ID AND SENS.FE_MAJOR_LEVEL_ID = derivedtbl_1.[SET]
    # WHERE (SENS.CAM = 1) AND (NOT (SENS.FE_MAJOR_LEVEL_ID IN (5,11,18,21,30,64)))) AS SENS2
		# GROUP BY DEPTH_STRATUM, SPATIAL_STRATUM, YEAR		ORDER BY DEPTH_STRATUM, SPATIAL_STRATUM


    Strata    <-   c(paste( "S", "\\textsubscript{1}", " (SWCVI)", sep='') , 
                     paste( "S", "\\textsubscript{2}", " (NWCVI)", sep='') ,
                     paste( "S", "\\textsubscript{3}", " (QCS)",   sep='') ,
                     paste( "S", "\\textsubscript{4}", " (SWCHG)", sep='') ,
                     paste( "S", "\\textsubscript{5}", " (NWCHG)", sep='') )
    Fm100250  <-   c(2,2,2,2,2)
    RD1       <-   c(2,0,0,1,2)
    Fm250450  <-   c(2,2,2,2,2)
    RD2       <-   c(2,2,1,0,3)
    Fm450750  <-   c(1,1,1,1,1)
    RD3       <-   c(0,1,1,1,1)
    Total     <-   c(5,5,5,5,5)  
    
    Totalyr    <-    c(RD1[1] + RD2[1] + RD3[1], RD1[2] + RD2[2] + RD3[2],
                     RD1[3] + RD2[3] + RD3[3], RD1[4] + RD2[4] + RD3[4],
                     RD1[5] + RD2[5] + RD3[5])
    
    datastrata<-   data.frame(Strata, Fm100250, RD1, Fm250450,RD2, Fm450750,RD3,Total,Totalyr)    

    LastLine  <-   c('', sum(datastrata$Fm100250), sum(datastrata$RD1),
                     sum(datastrata$Fm250450), sum(datastrata$RD2),
                     sum(datastrata$Fm450750), sum(datastrata$RD3),
                     sum(datastrata$Total) ,sum(datastrata$Total))
   
    datastrata <- rbind(datastrata, LastLine)
    datastrata$Strata <- as.character(datastrata$Strata)
    datastrata$Strata[6]  <- "Total"
    datastrata$Fm100250<-as.character(datastrata$Fm100250)
    datastrata$Fm250450<-as.character(datastrata$Fm250450)
    datastrata$Fm450750<-as.character(datastrata$Fm450750)  
    datastrata$RD1     <-as.character(datastrata$RD1)
    datastrata$RD2     <-as.character(datastrata$RD2)
    datastrata$RD3     <-as.character(datastrata$RD3) 
    datastrata$Total   <-as.character(datastrata$Total)     
 

    colnames(datastrata) <- c("Strata", paste("RD", "\\textsubscript{1}", sep='') , 
                              paste("RD", "\\textsubscript{1}"," 2022", sep=''), 
                                        paste("RD", "\\textsubscript{2}", sep='') , 
                              paste("RD", "\\textsubscript{2}"," 2022", sep=''),
                                        paste("RD", "\\textsubscript{3}", sep='') , 
                              paste("RD", "\\textsubscript{3}"," 2022", sep=''), 
                                          "Total", "Total 2022") 
   
       kableExtra::kable(datastrata, booktabs = TRUE,
                         linesep = "",
                         align = c("l","c","c","c","c","c","c","c","c"),
                         format = "latex",
                         escape = F, # allows textsubscript latex
                         caption = "(ref:table2Caption)") %>%
              row_spec(0,    bold = T) %>%
              row_spec(5, hline_after = T) %>%
              column_spec(1, width  = "3.3cm") %>%
              column_spec(2, width  = "1.1cm") %>%
              column_spec(3, width  = "0.7cm", color="blue" ) %>%
              column_spec(4, width  = "1.0cm") %>%
              column_spec(5, width  = "0.7cm", color="blue") %>% 
              column_spec(6, width  = "1.0cm") %>% 
              column_spec(7, width  = "0.7cm", color="blue") %>% 
              column_spec(8, width  = "0.7cm") %>%          
              column_spec(9, width  = "0.7cm", color="blue") %>%
                row_spec(0, color="black") %>%
              row_spec(6, bold=T) %>%
              add_header_above(c(" "= 1, "Sets in Depth Strata" = 6, " " = 2), bold=T) %>%
       kableExtra::kable_styling(font_size = 9, position = "left",latex_options = "hold_position")
    

```

(ref:table3Caption) Details of completed 60 trap camera movement sets. Seabird temperature and pressure recorder (SBE39), Actigraph accelerometer (AXL) and camera (CAM) are indicated with an 'x'.

```{r table3,  echo=FALSE}

  trap60 <- paste("SELECT YEAR, TRIP_ID, set_no, becket_no, trap_no, MAX(SBE39) AS SBE39, MAX(HOBO) AS HOBO,  ",
                  " MAX(CAM) AS CAM ",
                  " FROM (SELECT  dbo.SURVEY_trips_vw.YEAR, FE.TRIP_ID, FE.FE_MAJOR_LEVEL_ID AS set_no,  ",
                  " FE.FE_SUB_LEVEL_ID AS becket_no,  ",
                  " FE.FE_MINOR_LEVEL_ID AS trap_no, CASE WHEN FE_EVENT_SENSOR_DESC  ",
                  " LIKE '%sbe39%' THEN 1 ELSE 0 END AS SBE39,  ",
                  " CASE WHEN FE_EVENT_SENSOR_DESC LIKE '%accelerometer%' THEN 1 ELSE 0 END AS HOBO,  ",
                  " CASE WHEN FE_EVENT_SENSOR_DESC LIKE '%ctd%' THEN 1 ELSE 0 END AS CTD,  ",
                  " CASE WHEN FE_EVENT_SENSOR_DESC LIKE '%camera%' THEN 1 ELSE 0 END AS CAM,  ",
                  " CASE WHEN FE_EVENT_SENSOR_DESC LIKE '%oxygen%' THEN 1 ELSE 0 END AS DO ",
                  " FROM  GFBioSQL.dbo.TRAP_SENSOR INNER JOIN ",
                  "  GFBioSQL.dbo.FE_EVENT_SENSOR ON GFBioSQL.dbo.TRAP_SENSOR.FE_EVENT_SENSOR_CODE =  ",
                  " GFBioSQL.dbo.FE_EVENT_SENSOR.FE_EVENT_SENSOR_CODE INNER JOIN ",
                  " GFBioSQL.dbo.FISHING_EVENT AS FE ON GFBioSQL.dbo.TRAP_SENSOR.FISHING_EVENT_ID =",
                  " FE.FISHING_EVENT_ID INNER JOIN ",
                  " dbo.SURVEY_trips_vw ON FE.TRIP_ID = dbo.SURVEY_trips_vw.TRIP_ID ",
                  " GROUP BY FE.TRIP_ID, FE.FE_MAJOR_LEVEL_ID, FE.FE_SUB_LEVEL_ID,  ",
                  " FE.FE_MINOR_LEVEL_ID, dbo.SURVEY_trips_vw.YEAR, ",          
                  " GFBioSQL.dbo.FE_EVENT_SENSOR.FE_EVENT_SENSOR_DESC  ", 
                  " HAVING  (dbo.SURVEY_trips_vw.YEAR = 2022) AND  ",  # provide year
                  " (FE.FE_MAJOR_LEVEL_ID IN (5,11,18,21,30,64))) AS SENS  GROUP BY YEAR, ",  #provide 60 trap sets
                  " TRIP_ID, set_no, becket_no, trap_no ",
                  " order by set_no, becket_no, trap_no", sep="")
    #trapcam  <- GetSQLData(trap60,"Sablefish")
    #write.table(trapcam, file = paste(path,"table3.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
    trapcam   <-  read.csv(paste(path,'table3.csv',sep=''), header=T)
    trapcam   <-  trapcam[,c(-1,-2)]
    Strata    <-  c(paste( "S", "\\textsubscript{1}", " (SWCVI)", sep=''), " ", " ", 
                    paste( "S", "\\textsubscript{1}", " (SWCVI)", sep=''), " ", " ", 
                    paste( "S", "\\textsubscript{1}", " (SWCVI)", sep=''), " ", " ", 
                    paste( "S", "\\textsubscript{1}", " (SWCVI)", sep=''), " ", " ", 
                    paste( "S", "\\textsubscript{2}", " (NWCVI)", sep=''), " ", " ", 
                    paste( "S", "\\textsubscript{5}", " (NWCHG)", sep=''), " ", " ")
    Trap.camera       <- cbind(Strata, trapcam)
    Trap.camera$set_no<- as.character(Trap.camera$set_no)
   
    Trap.camera$SBE39 <- as.character(Trap.camera$SBE39)
    Trap.camera$HOBO  <- as.character(Trap.camera$HOBO)
    Trap.camera$CAM   <- as.character(Trap.camera$CAM)
    Trap.camera$SBE39 <- "x"
    Trap.camera$HOBO  <- "x"
    Trap.camera$CAM   <- "x"
    Trap.camera$set_no<- cleanf(Trap.camera$set_no)
    
    colnames(Trap.camera)  <- c( "Spatial Strata", "Set", "Becket id" , "Trap id", "SBE39", "AXL", "CAM")
    
    kableExtra::kable(Trap.camera, booktabs = TRUE, linesep = "",
                      align = c("l","r","r","r","c","c","c"),
                      escape = F, # allows textsubscript latex
                      format = "latex",
                      caption = "(ref:table3Caption)") %>%
                      row_spec(0,    bold = T) %>%
                      row_spec(c(3,6,9,12,15), hline_after = T) %>%
                      
    kableExtra::kable_styling(font_size = 9, position = "left",latex_options = "hold_position")

```
\clearpage

(ref:table4Caption) Summary of species captured during the `r yr` survey StRS sets conducted by the `r boat`. No value in both weight and count fields indicate trace weights.

```{r table4,  echo=FALSE}

    options(knitr.kable.NA = '')
    dtSP   <- paste("exec procRReport_SpeciesSummary ",yr," ,'StRS'",sep="")
    #datSP  <- GetSQLData(dtSP,"Sablefish")
    #write.table(datSP, file = paste(path,"table4.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
    datSP  <-  read.csv(paste(path,'table4.csv',sep=''), header=T)
    datSP$Total_weight     <- formatC(datSP$Total_weight, format="d", big.mark=",") 
       
    dat1SP <- datSP[,c(-1)] 
    dat1SP <- dat1SP[,c(-3)]
    dat1SP <- dat1SP[,c(-2)]
    dat1SP <- dat1SP[,c(-6)]  # trim columns
    cleandataSP<-dat1SP
    cleandataSP$Summary_sp     <- cleanf(cleandataSP$Summary_sp)  #  remove duplicates function
    cleandataSP$Common_Name    <- stringr::str_to_title(as.character(cleandataSP$Common_Name))
    cleandataSP$Common_Name    <- gsub("Spiny Dogfish","North Pacific Spiny Dogfish", cleandataSP$Common_Name)
    cleandataSP$Total_weight   <- gsub("NA", "", cleandataSP$Total_weight)
    colnames(cleandataSP)      <- c( "Category", "Common Name", "Scientific Name" , "Count", "Weight(kg)")
    cleandataSP[25,2]          <- "Fragile Sea Urchin"
    
    
    kableExtra::kable(cleandataSP,
                      booktabs = TRUE,linesep = "",
                      align = c("l","l","l","l","l"),
                      format = "latex",  caption = "(ref:table4Caption)") %>%
                      row_spec(0,  bold = T) %>%
                      row_spec(8,  hline_after = T) %>%
                      row_spec(20, hline_after = T) %>%
                      row_spec(23, hline_after = T) %>%
                      kableExtra::kable_styling(font_size = 8, position = "left",
                                                latex_options = "hold_position")
```
\clearpage

(ref:table5Caption) Summary of species captured by the `r boat` during the `r yr` survey standardized sets conducted at Finlayson inlet locality. No value in both weight and count fields indicate trace weights.

```{r table5, echo=FALSE}

  options(knitr.kable.NA = '')
  dtSP   <- paste("exec procRReport_SpeciesSummary ",yr," ,'INLET STANDARDIZED'",sep="")
  #datSP.summ  <- GetSQLData(dtSP,"Sablefish")
  #write.table(datSP.summ, file = paste(path,"table5.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
  datSP.summ   <-  read.csv(paste(path,'table5.csv',sep=''), header=T)
  
  dat1SP <- datSP.summ[,c(-1)] 
  dat1SP <- dat1SP[,c(-3)]
  dat1SP <- dat1SP[,c(-2)]
  dat1SP <- dat1SP[,c(-6)]
  cleandataSPi<-dat1SP
  cleandataSPi$Summary_sp <- cleanf(cleandataSPi$Summary_sp)  #use the remove duplicates function
  cleandataSPi$Common_Name    <- stringr::str_to_title(as.character(cleandataSPi$Common_Name))
  colnames(cleandataSPi)  <- c( "Category", "Common Name", "Scientific Name" , "Count", "Weight(kg)")

  kableExtra::kable(cleandataSPi,
                    booktabs = TRUE,linesep = "",
                    align = c("l","l","l","l","l"),
                    format = "latex",  caption = "(ref:table5Caption)") %>%
                    row_spec(0,  bold = T) %>%
                    row_spec(1,  hline_after = T) %>%
                    row_spec(2,  hline_after = T) %>%
                    kableExtra::kable_styling(font_size = 8, position = "left",latex_options = "hold_position")

```


(ref:table6Caption) Summary of Sablefish sex ratios and mean fork length measurements collected during the `r yr` stratified random sets by spatial and depth stratum.

```{r table6, echo=FALSE}

    newdata2       <-   read.csv(paste(path,'table6.csv',sep=''), header=T)  # created in results section
    data_mod1      <-   read.csv(paste(path,'table6a.csv',sep=''),header=T) # created in results section
    # head(newdata2)
    data_mod1[4,1] <-"S1"
    data_mod1[4,2] <-"RD"
    data_mod1[8,1] <-"S2"
    data_mod1[8,2] <-"RD"
    data_mod1[12,1] <-"S3"
    data_mod1[12,2] <-"RD" 
    data_mod1[16,1] <-"S4"
    data_mod1[16,2] <-"RD" 
    data_mod1[20,1] <-"S5"
    data_mod1[20,2] <-"RD"  
    
    data_mod1$Depth <- gsub("RD1       ","RD1",data_mod1$Depth)
    data_mod1$Depth <- gsub("RD2       ","RD2",data_mod1$Depth)
    data_mod1$Depth <- gsub("RD3       ","RD3",data_mod1$Depth)
    
    data_mod <- cbind(data_mod1[1:2], stack(data_mod1[3:4]))
    data_mod$label <- paste(data_mod$Spatial, data_mod$Depth, sep='')
    #print(data_mod)
    big.value <- 1

    w<- data_mod %>%
        group_by(Spatial,Depth) %>%
     do({
       p <- ggplot(., aes(x = Spatial, y = values, fill=ind)) + 
            geom_bar(stat="identity", position = position_dodge(), width=0.8,alpha = 0.5) + guides(fill=FALSE)  +
            scale_fill_manual(values = c("Females" = "#0084A8",
                                         "Males" = "#00cc99"))  +
         ylim(0, big.value) +
         theme_void() 
         #ggsave(p, filename = paste0(path, "bar_", unique(.$label), ".png"), 
          #     width = 0.2, height = 0.21)  # create many small figures
         invisible(.) 
     })
    
    newdata2$label <- paste(data_mod1$Spatial, data_mod1$Depth, sep='')  #get labels from other table

    newdata2[1,1] <-   paste( "S", "\\textsubscript{1}", sep='')
    newdata2[5,1] <-   paste( "S", "\\textsubscript{2}", sep='')
    newdata2[9,1] <-   paste( "S", "\\textsubscript{3}", sep='')
    newdata2[13,1] <-  paste( "S", "\\textsubscript{4}", sep='')
    newdata2[17,1] <-  paste( "S", "\\textsubscript{5}", sep='')
    
    newdata2[1,2] <-   paste( "RD", "\\textsubscript{1}", sep='')
    newdata2[2,2] <-   paste( "RD", "\\textsubscript{2}", sep='')
    newdata2[3,2] <-   paste( "RD", "\\textsubscript{3}", sep='')
    
    newdata2[5,2] <-   paste( "RD", "\\textsubscript{1}", sep='')
    newdata2[6,2] <-   paste( "RD", "\\textsubscript{2}", sep='')
    newdata2[7,2] <-   paste( "RD", "\\textsubscript{3}", sep='')
    
    newdata2[9,2] <-   paste( "RD", "\\textsubscript{1}", sep='')
    newdata2[10,2] <-  paste( "RD", "\\textsubscript{2}", sep='')
    newdata2[11,2] <-  paste( "RD", "\\textsubscript{3}", sep='')

    newdata2[13,2] <-  paste( "RD", "\\textsubscript{1}", sep='')
    newdata2[14,2] <-  paste( "RD", "\\textsubscript{2}", sep='')
    newdata2[15,2] <-  paste( "RD", "\\textsubscript{3}", sep='')   

    newdata2[17,2] <-  paste( "RD", "\\textsubscript{1}", sep='')
    newdata2[18,2] <-  paste( "RD", "\\textsubscript{2}", sep='')
    newdata2[19,2] <-  paste( "RD", "\\textsubscript{3}", sep='') 
    
    newdata2 <-  newdata2 %>%
                mutate(Sparkline = 
                       paste0("\\raisebox{.01\\height} {\\includegraphics[width=0.4cm]{",path,"bar_",unique(.$label),".png}}") )
    
    newdata3  <-  newdata2[,c(1,2,9,3,4,5,6,7),] 
    names(newdata3) <- c("Spatial","Depth", "barpolt","Males","Females","Males","Females", "Tagged")
      
    kableExtra::kable(newdata3, row.names = FALSE,
                booktabs = TRUE,   linesep = "", escape = F, # allows textsubscript latex
                format = "latex",  caption = "(ref:table6Caption)") %>%
      
        add_header_above(c( "Strata"= 2,
                            "Proportion" = 3, 
                            "Mean Fork Length (mm)" = 3),bold=T) %>%  
      
    kableExtra::kable_styling(font_size = 9, position = "left", latex_options = "hold_position") %>%
                row_spec(0,    bold = T) %>%
                row_spec(3,    hline_after = T) %>%
                row_spec(4,    bold = T, hline_after = T) %>%
                row_spec(7,    hline_after = T) %>% 
                row_spec(8,    bold = T, hline_after = T) %>%      
                row_spec(11,   hline_after = T) %>%
                row_spec(12,   bold = T, hline_after = T) %>%      
                row_spec(15,   hline_after = T)   %>% 
                row_spec(16,   bold = T, hline_after = T) %>%   
                row_spec(19,   hline_after = T)   %>% 
                row_spec(20,   bold = T)
     
    
  
      
```
\clearpage

(ref:table7Caption) Canadian tag recovery counts from all sets during the 2021 survey, by distance from release site and years at liberty. Distances were determined using the great circle distance between the release location and recovery location.


```{r table7, echo=FALSE}

      tag  <- paste("select * from Report_Survey_Tag_Recoveries",sep="") # have to go in database and change the year value
      #tag.rec <- GetSQLData(tag,"FishTag")
      #write.table(tag.rec, file = paste(path,"table7.csv",sep=''),row.names=FALSE, na="",col.names=TRUE, sep=",")
      tag.rec <-  read.csv(paste(path,'table7.csv',sep=''), header=T)
      
      tag.rec[is.na(tag.rec)] <- 0   # convert NA to zero in whole table
      tag.rec$YearGroups      <- as.character(tag.rec$YearGroups)  # change column to character
      tag.rec$YearGroups      <- gsub("Grp1.", "", tag.rec$YearGroups)
      tag.rec$YearGroups      <- gsub("Grp2.", "", tag.rec$YearGroups)
      tag.rec$YearGroups      <- gsub("Grp3.", "", tag.rec$YearGroups)  
      tag.rec$YearGroups      <- gsub("Grp4.", "", tag.rec$YearGroups)      
      tag.rec$Recoveries      <- as.numeric(rowSums(tag.rec[,2:8], na.rm=TRUE))
      
      ad.row <- c('Total Counts',sum(tag.rec$X.10.km), sum(tag.rec$X11.50.km), sum(tag.rec$X51.100.km),
                                 sum(tag.rec$X101.250.km), sum(tag.rec$X251.500.km), sum(tag.rec$X501.1000.km),
                                 sum(tag.rec$X.1000.km), sum(tag.rec$Recoveries) )
      tag.rec2 <- rbind(tag.rec,ad.row) 

      names(tag.rec2) <- c("Years at Liberty","<10","11-50","51-100","101-250","251-500","501-1000","1000+","Recovery count")
   
      kableExtra::kable(tag.rec2, row.names = FALSE,
                        align = c("l","l","l","l","l","l","l","l","l"),
                  booktabs = TRUE,   linesep = "",
                  format = "latex",  caption = "(ref:table7Caption)") %>% 
      add_header_above(c(" "= 1,
                        "Distance (km) from Release Location" = 7, 
                        " " = 1),bold=T) %>% 
      
       kableExtra::kable_styling(font_size = 9, position = "left", latex_options = "hold_position") %>%
                row_spec(0, bold = T) %>%
                row_spec(4, hline_after = T) %>%
                column_spec(2, width  = "1.1cm") 

```
\clearpage




