<!-- The following code should appear at the beginning of the first appendix.
(if you have one)
After that, all subsequent sections will be turned into appendices. -->

`r if(knitr:::is_latex_output()) '% begin csasdown appendix'`
`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

\clearpage

# LIST OF SABLEFISH RESEARCH AND ASSESSMENT SURVEYS. {#app:first-appendix}

```{r appendixA, results="asis"}

   dtBW   <- paste('exec dbo.procRKnitr_SurveyTrips ', yr ,sep='')
   #trip   <- GetSQLData(dtBW,"Sablefish")
   #write.table(trip, file = paste(path,'appendixA.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
   trip   <-  read.csv(paste(path,'appendixA.csv',sep=''),header=T)
   
   colnames(trip) <- c("Year", "Dates",  "Vessel", "Captain", "Set Count", "GFBIO Trip id")
   kableExtra::kable(trip,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     format = "latex")  %>%
   kableExtra::kable_styling(font_size = 8) %>% 
                     row_spec(0, bold = T)

```
\clearpage

# SURVEY SET DETAILS `r yr`. {#app:second-appendix}
Details of sets completed during the `r yr` survey program (F/V `r boat`).  Sets are listed by stratum/inlet name, set type, depth stratum, start date, end of gear deployment time and duration in minutes. The depth strata for type 3 tagging sets include RD~1~ (100-250 fathoms), RD~2~ (250-450 fathoms) and RD~3~ (450-750 fathoms). The position data includes the major area and start and end latitude and longitude in degrees decimal minutes. The bottom depths (in meters) of the fishing set are shown with the mean bottom depth calculated from recordings at one minute intervals between the start and end of the set. The number of traps fished for each set excludes open traps, while holed or fouled traps have been included.  Sets that successfully deployed a Seabird SBE temperature and pressure recorder (SBE 39), an accelerometer (AXL) or a camera (CAM) are indicated with an 'x'. 


```{r appendixB, results="asis"}

    library(kableExtra)
    library(ggplot2)
  
    setcnt     <-   110
    options(knitr.kable.NA = '')  # get rid of NAs
    srvyset    <-  paste('dbo.procRReport_Survey_SetDetails ', yr,',1,',setcnt, sep='')
    # survey set details include the table from    exec dbo.Build_Seabird_tables
    # named Report_SBE_HOBO_IND 
    #srvy.set   <-  GetSQLData(srvyset,"Sablefish")
    #write.table(srvy.set, file = paste(path,'appendixB.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
    srvy.set   <-  read.csv(paste(path,'appendixB.csv',sep=''),header=T)
    
    # no ctd in 2022
    srvy.set  <-   srvy.set[,c(-23)]  
    latcnt  <-  length(srvy.set[, 9])  # add degree symbol in lat and long values
               for (i in 1:latcnt)
                      { srvy.set[i,9]= paste(srvy.set[i,9],'째 ', srvy.set[i,10],"'N",sep="")  }
    latcnt  <-  length(srvy.set[,11])
               for (i in 1:latcnt)
                      { srvy.set[i,11]=paste(srvy.set[i,11],'째 ', srvy.set[i,12],"'W",sep="") }
    latcnt  <-  length(srvy.set[,13])
               for (i in 1:latcnt)
                      { srvy.set[i,13]=paste(srvy.set[i,13],'째 ', srvy.set[i,14],"'N",sep="") }
    latcnt<-length(srvy.set[,15])
               for (i in 1:latcnt)
                      { srvy.set[i,15]=paste(srvy.set[i,15],'째 ', srvy.set[i,16],"'W",sep="") }
   
    # srvy.set  <-  srvy.set[,c(-22,-23,-24)]  # no hobo, ctd or camera columns needed 2021
    # head(srvy.set)
    srvy.set  <-  srvy.set[,c(-10,-12,-14,-16)]  
   
   
    colnames(srvy.set) <- c( "Set", "Spatial Stratum","Type",      
                             "Depth Stratum",   "Date", "Time", 
                             "Duration (minutes)",  "Area", 
                             "Start Latitude",  "Start Longitude", 
                             "End Latitude",    "End Longitude", 
                             "Start Depth (m)", "End Depth (m)", "Mean Depth (m)", 
                             "Traps Fished",    "SBE 39", "AXL", "CAM")
   
    srvy.set$Type <- as.character(srvy.set$Type)
    #-- unique to 2022 sets 5,11,18,21,30,64 are Movement sets
    srvy.set$Type[srvy.set$Set==5]  <-  'Movement'
    srvy.set$Type[srvy.set$Set==11] <-  'Movement'  
    srvy.set$Type[srvy.set$Set==18] <-  'Movement'
    srvy.set$Type[srvy.set$Set==21] <-  'Movement' 
    srvy.set$Type[srvy.set$Set==30] <-  'Movement'    
    srvy.set$Type[srvy.set$Set==64] <-  'Movement'  
   
    #prep images
    trap.set         <-  srvy.set[ ,c(-2,-4:-24), ]
    names(trap.set)  <-  c("surveyset","Type")
     
    trap.set$count   <- 81
    trap.set         <- trap.set %>%  # set background colour
                         mutate(get.color = ifelse(Type %in% c("Inlet") , "olivedrab1",  "white"))
    trap.set$get.color[trap.set$Type=='Movement']   <- "lightskyblue"   # movement
    trap.set$get.color[trap.set$surveyset %in% 
                         c(6,12,19,23,31,37,38,43,44,70,75,76,82,83,84,90,91)] <- "plum2"  
    # tail(trap.set)
    
     w   <-  trap.set %>%
     group_by(surveyset) %>%
     do({
       p <- ggplot(., aes(y = count, x = 1, label=.$surveyset)) + 
              geom_bar(stat="identity", color="white",fill=.$get.color) +
                 ylim(0, 100) +
                 theme_void() +
                 geom_text(size=8,vjust = 1.3)
      ggsave(p, filename = paste0(path,"sets_", unique(.$surveyset), ".png"), width = 1.2, height = 0.5)  
      invisible(.) })
 
      kableExtra::kable(srvy.set,
                    booktabs  = TRUE, 
                    align = c("l","l","l","l","l","l","l","l","l","l","l","l","l","l","l","l","l","l","l"),
                    longtable = T,
                    linesep   = "",
                    escape = F,
                    format    = "latex") %>%
      
   kableExtra::kable_styling(font_size = 8, latex_options = "repeat_header",
               repeat_header_text = "continued.", 
               repeat_header_method = "replace") %>%
   kableExtra::landscape() %>%
    
   row_spec(0, bold = T)  %>%     
   column_spec(1,width    = "0.5cm") %>%  # set
   column_spec(2,width    = "1.3cm") %>%  # stratum
   column_spec(3,width    = "0.9cm") %>%  # type 
   column_spec(4,width    = "0.7cm") %>%  # depth stratum
   column_spec(5,width    = "0.9cm") %>%  # date
   column_spec(6,width    = "0.6cm") %>%  # time      
   column_spec(7,width    = "0.9cm") %>%  # dur
   column_spec(8,width    = "0.5cm") %>%  # area   
   column_spec(9,width    = "1.2cm") %>%  # start lat
   column_spec(10,width   = "1.6cm") %>%  # start long
   column_spec(11,width   = "1.2cm") %>%  # end lat
   column_spec(12,width   = "1.6cm") %>%  # end long
   column_spec(13,width   = "0.6cm") %>%  # start dep
   column_spec(14,width   = "0.6cm") %>%  # end dep    
   column_spec(15,width   = "0.5cm") %>%  # mean dep
   column_spec(16,width   = "0.6cm") %>%  # tf
   column_spec(17,width   = "0.4cm") %>%  # sbe
   column_spec(18,width   = "0.4cm") %>%  # hobo
   column_spec(19,width   = "0.4cm") %>%  # cam   
   sub("\\caption\\[\\]\\{\\}", "\\caption*{}", .)
``` 

\clearpage

# SUMMARY OF BASKET USE BY TRAP `r yr`.{#app:third-appendix} 

Summary of the basket use by trap number for StRS and inlet sets during the `r yr` Sablefish survey. The fate of the Sablefish catch for each set and trap is indicated using the following abbreviations: D = Discarded after weighing (processed as commercial catch), A = Sampled for LSMWO, T = Tagged and released, SD = Sublegal discarded, F= Frames, NULL = No Sablefish catch/trap missing. Standardized sets at mainland inlet localities are highlighted with green colour and StRS sets have no background colour. Those set numbers highlighted with purple colour had a camera deployed on the string of gear.  

```{r appendixC, echo=FALSE}

   # Sablefish.dbo.procRReport_Survey_TrapUse procedure pulls 
   # data from table dbo.GFBIO_TRAPS_USE  
   # created by procedure Sablefish.dbo.Build_BIO_Sablefish_Tables
   # always double check for trap 26

   options(knitr.kable.NA = '')
   trap       <- paste("dbo.procRReport_Survey_TrapUse ",yr,",1,",setcnt, sep="")
   #trap.dat    <- GetSQLData(trap,"Sablefish")
   #write.table(trap.dat, file = paste(path,'appendixC.csv',sep=''),row.names=FALSE,na="",col.names=TRUE,sep=",")    
   trap.dat    <- read.csv(paste(path,'appendixC.csv',sep=''),header=T)
   
   trap.Usage    <- trap.dat[,c(-1)]      # delete trip_id
   trap.Usage    <- trap.Usage[,c(-28)]   # delete Trap 27, there are many sets with 26 traps in 2022

   trap.Usage    <- dplyr::mutate(trap.Usage, A = rowSums(trap.Usage == "A", na.rm = TRUE))  # add up A's
   trap.Usage    <- dplyr::mutate(trap.Usage, AF = rowSums(trap.Usage == "A,F", na.rm = TRUE)) 
   trap.Usage$A2 <- trap.Usage$A + trap.Usage$AF
   
   trap.Usage    <- dplyr::mutate(trap.Usage, D = rowSums(trap.Usage == "D", na.rm = TRUE))  # add up D's     
   trap.Usage    <- dplyr::mutate(trap.Usage, DF = rowSums(trap.Usage == "D,F", na.rm = TRUE))  
   trap.Usage$D2 <- trap.Usage$D + trap.Usage$DF  
   
   trap.Usage    <- dplyr::mutate(trap.Usage, T = rowSums(trap.Usage == "T", na.rm = TRUE))  # add up T's
   trap.Usage    <- dplyr::mutate(trap.Usage, TF = rowSums(trap.Usage == "T,F", na.rm = TRUE))  
   trap.Usage$T2 <- trap.Usage$T + trap.Usage$TF     
   
   trap.Usage    <- dplyr::mutate(trap.Usage, N = rowSums(trap.Usage == "" , na.rm = TRUE))  # add up Nulls
   trap.Usage$N  <- trap.Usage$N-1

   trap.Usage    <- trap.Usage[,c(-28,-29,-31,-32,-34,-35)]  # trim unnecessary columns
   trap.Usage    <- trap.Usage[c(-7,-14,-27,-63),]

   # add in sparkline 
   trap.Usage  <-  trap.Usage %>%    
                   mutate(Survey.set= paste0(
                                      "\\raisebox{-.28\\height} {\\includegraphics[width=0.8cm]{",path,"sets_",Set,".png}}") )
   # reorder table
   trap.Usage  <- trap.Usage[, c(32,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31)]  
 
   names(trap.Usage)  <-  c("Set","1","2","3","4","5","6","7","8","9","10",
                            "11","12","13","14","15","16","17",
                            "18","19","20","21","22","23","24", 
                            "25","26", "A","D","T","-")

   kableExtra::kable(trap.Usage,
                     booktabs = TRUE, 
                     longtable = T,
                     escape = F,        # lets the image show up 
                     linesep   = "",
                     row.names = FALSE,  # gets rid of matrix counter
                     format = "latex") %>%
      
      add_header_above(c(" "= 1,
                      "Trap" = 26,
                      "Total"=4
                      ), bold = TRUE) %>%     
      
   kableExtra::kable_styling(font_size = 6, 
                     latex_options = "repeat_header",
                     repeat_header_text = "continued.", 
                     repeat_header_method = "replace") %>%  
      
   kableExtra::landscape()  %>%
       row_spec(0, bold=T) %>%
       column_spec(1,width      = "0.8cm") %>%
       column_spec(2,width      = "0.3cm") %>%
       column_spec(3,width      = "0.3cm") %>%
       column_spec(4,width      = "0.3cm") %>%
       column_spec(5,width      = "0.3cm") %>%
       column_spec(6,width      = "0.3cm") %>%
       column_spec(7,width      = "0.3cm") %>%
       column_spec(8,width      = "0.3cm") %>%   
       column_spec(9,width      = "0.3cm") %>%   
       column_spec(10,width     = "0.3cm") %>%
       column_spec(11,width     = "0.4cm") %>%
       column_spec(12,width     = "0.4cm") %>%
       column_spec(13,width     = "0.4cm") %>%
       column_spec(14,width     = "0.4cm") %>%
       column_spec(15,width     = "0.4cm") %>%
       column_spec(16,width     = "0.4cm") %>%
       column_spec(17,width     = "0.4cm") %>%
       column_spec(18,width     = "0.4cm") %>%
       column_spec(19,width     = "0.4cm") %>%
       column_spec(20,width     = "0.4cm") %>%
       column_spec(21,width     = "0.4cm") %>%  
       column_spec(22,width     = "0.4cm") %>% 
       column_spec(23,width     = "0.4cm") %>%       
       column_spec(24,width     = "0.4cm") %>% 
       column_spec(25,width     = "0.4cm") %>%
       column_spec(26,width     = "0.4cm") %>%      
       column_spec(27,width     = "0.4cm")  %>% 
       column_spec(28,width     = "0.2cm") %>%
       column_spec(29,width     = "0.2cm") %>%
       column_spec(30,width     = "0.2cm") %>%      
       column_spec(31,width     = "0.2cm") 
```
\clearpage

```{r appendixDSetUp, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}

    #library(pander)

    trap.count <-paste(
                 " select tp.YEAR, fe.TRIP_ID, fe.FE_MAJOR_LEVEL_ID AS SET_ID,  ",
                 " fe.FE_SUB_LEVEL_ID AS BECKET, ", 
                 " fe.FE_MINOR_LEVEL_ID AS TRAP, SUM(c.CATCH_COUNT) AS total_count ",
                 " from dbo.GFBIO_TRAP_VW_VW AS fe INNER JOIN ",
                 " (select YEAR, TRIP_ID from dbo.SURVEY_trips_vw ",
                 " group by YEAR, TRIP_ID) AS tp ON fe.TRIP_ID = tp.TRIP_ID LEFT OUTER JOIN ",
                 " GFBioSQL.dbo.TRAP_SPECS AS ts ON fe.FISHING_EVENT_ID = ts.FISHING_EVENT_ID LEFT OUTER JOIN ",
                 " (select FISHING_EVENT_ID, SUM(CASE WHEN BAIT_LURE_CODE = 15 AND BAIT_METHOD_CODE = 4  ",
                 " then TRPBL_BAIT_AMOUNT ELSE NULL END) AS BAGGED_SQUID, SUM(CASE WHEN BAIT_LURE_CODE = 18 and  ", 
                 " BAIT_METHOD_CODE = 6 THEN TRPBL_BAIT_AMOUNT ELSE NULL END) AS LOOSE_HAKE,  ",
                 " SUM(CASE WHEN (BAIT_LURE_CODE <> 15 AND BAIT_METHOD_CODE <> 4) AND (BAIT_LURE_CODE <> 18 AND  ",
                 " BAIT_METHOD_CODE <> 6) THEN TRPBL_BAIT_AMOUNT ELSE NULL END) AS OTHER_BAIT ",
                 " from GFBioSQL.dbo.TRAP_BAIT_LURE ",
                 " group by FISHING_EVENT_ID) AS bait ON fe.FISHING_EVENT_ID = bait.FISHING_EVENT_ID  ",
                 " LEFT OUTER JOIN ",
                 " (select fec.FISHING_EVENT_ID, GFBioSQL.dbo.CATCH.SPECIES_CODE,  ",
                 " SUM(GFBioSQL.dbo.CATCH.CATCH_WEIGHT) AS CATCH_WEIGHT, ",
                 " SUM(GFBioSQL.dbo.CATCH.CATCH_COUNT) AS CATCH_COUNT,  ",
                 " AVG(ISNULL(GFBioSQL.dbo.CATCH.CATCH_VERIFICATION_CODE, 0)) AS VERIFICATION_METHOD ",
                 " from GFBioSQL.dbo.FISHING_EVENT_CATCH AS fec INNER JOIN ",
                 " GFBioSQL.dbo.CATCH ON fec.CATCH_ID = GFBioSQL.dbo.CATCH.CATCH_ID ",
                 " where (GFBioSQL.dbo.CATCH.SPECIES_CODE = '455') ",
                 " GROUP BY fec.FISHING_EVENT_ID, GFBioSQL.dbo.CATCH.SPECIES_CODE) ",
                 " AS c ON fe.FISHING_EVENT_ID = c.FISHING_EVENT_ID ",
                 " GROUP BY fe.FE_MAJOR_LEVEL_ID, fe.TRIP_ID, tp.YEAR, ",
                 " fe.FE_SUB_LEVEL_ID, fe.FE_MINOR_LEVEL_ID",
                 " having  (tp.YEAR IN ('", yr ,"')) order by SET_ID, BECKET, TRAP",sep="")
    
    #trap.sable1   <- GetSQLData(trap.count,"Sablefish")
    #write.table(trap.sable1, file = paste(path,"appendixDSetUp.csv",sep=''),
    #          row.names=FALSE, na="",col.names=TRUE, sep=",")
    trap.sable1  <-  read.csv(paste(path,'appendixDSetUp.csv',sep=''), header=T)
    trap.sable25 <-  trap.sable1[!trap.sable1$SET_ID %in% c(5,11,18,21,30,64),]  # 60 TRAP SETS SO HUGE THEY NOT SHOWN
    #unique(trap.sable25$SET_ID)
   
    library(tidyverse)
    library(tidyr)
    library(scales)

    trap.sable <- trap.sable25[,c(-1,-2,-4)] 
    #trap.sable$SET_ID <- as.factor(trap.sable$SET_ID)
    names(trap.sable) <- c("SurveySet","Trap","Value")
    trap.sable[is.na(trap.sable)] <- 0
   
   # --- unique to 2022 until HAUL_POSITION_CODE is populated, sets 95,96,97 = start
   
   new.trap.sable <- trap.sable %>% mutate(PU = ifelse(SurveySet %in% c(95,96,97), "START", "END"))

   trap.sable.start <- new.trap.sable[new.trap.sable$PU =='START',]
   trap.sable.end   <- new.trap.sable[new.trap.sable$PU =='END',]
   big.value <- max(new.trap.sable$Value)

   w<-trap.sable.start %>%   # create sparkline graphs
     group_by(SurveySet) %>%
     do({
       p <- ggplot(., aes(x = Trap, y = Value)) + 
            geom_area( fill="#6495ED", alpha=0.4) + 
            #geom_area( fill=trap.sable$col, alpha=0.4) + 
            geom_line(linewidth = 4, color="blue") +      
            #geom_point(size=15, color="red") + 
            ylim(0, big.value) +
            xlim(0,25) +
            theme_void() 
            stat_summary(fun = max, colour = "red", geom = "point", size = 5)
            ggsave(p, filename = paste0(path, "fig", unique(.$SurveySet), ".png"), width = 8, height = 1.9)  # mini graphs
            invisible(.) 
       })
   
    w<-trap.sable.end %>%   # create sparkline graphs
     group_by(SurveySet) %>%
     do({
       p <- ggplot(., aes(x = Trap, y = Value)) + 
            geom_area( fill="green", alpha=0.4) + 
            #geom_area( fill=trap.sable$col, alpha=0.4) + 
            geom_line(linewidth = 4, color="dark green") +      
            #geom_point(size=15, color="red") + 
            ylim(0, big.value) +
            xlim(0,25) +
            theme_void() 
            stat_summary(fun = max, colour = "red", geom = "point", size = 5)
            ggsave(p, filename = paste0(path,"fig", unique(.$SurveySet), ".png"), width = 8, height = 1.9)  # mini graphs
            invisible(.) 
       
     })


```
\clearpage

# SUMMARY OF SABLEFISH BIOLOGICAL DATA `r yr`. {#app:fourth-appendix}

Summary of biological data collected for Sablefish by set, catch weight in kilograms and numbers of fish.  Sablefish counts by trap are represented by sparklines, with every string picked up from the end location in 2021. Tagged fish counts are recorded by number of fish recovered and re-released, fish sampled and fish tagged and released. Tagged fish fork lengths are listed by count and mean (millimeters). Specimen counts are listed by sample type; mean fork lengths are tabulated.  Standardized sets at mainland inlet localities are highlighted with green colour and StRS sets have no background colour. Those set numbers highlighted with purple colour had a camera deployed on the string of gear.  The 4 sets highlighted in blue colour represent the 60 trap sets that were deployed to evaluate gear bottom-contact.

```{r appendixD, echo=FALSE}

   #  Sablefish.dbo.procReport_Survey_SampleDetails pulls data 
   #  from table GFBIO_RESEARCH_SAMPLE_DETAILS, built by     
   #  procedure Sablefish.dbo.Build_BIO_Sablefish_Tables 
   # \renewcommand{\arraystretch}{1} # use above r code to stretch table

   # build tag to finish this table.....

   samples            <-  paste("dbo.procReport_Survey_SampleDetails ",yr,",1,",setcnt, sep="")
   #surveyspec          <-  GetSQLData(samples,"Sablefish")
   #write.table(surveyspec, file = paste(path,'appendixD.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")  
   surveyspec          <-  read.csv(paste(path,'appendixD.csv',sep=''),header=T)
   surveyspec.count.row.total   <-  length(surveyspec$SET)
   surveyspec          <-  surveyspec[c(-surveyspec.count.row.total),]
   #tail(surveyspec)

   # camera/movement sets
   surveycam                        <-  surveyspec[c(7,14,27,63),]
   surveycam.Total.Count            <-  sum(surveycam$Total.Count)
   surveycam.Recovered.Dead.Number  <-  sum(surveycam$Recovered.Dead.Number)
   surveycam.Fork.Len.Tag.Sample.Count<-  sum(surveycam$Fork.Len.Tag.Sample.Count)
   surveycam.Fork.Len.Sample.Count  <-  sum(surveycam$Fork.Len.Sample.Count)
   surveycam.Sex.Sample.Count       <-  sum(surveycam$Sex.Sample.Count)
   surveycam.Maturity.Sample.Count  <-  sum(surveycam$Maturity.Sample.Count) 
   surveycam[is.na(surveycam)] <- 0
   surveycam.Otolith.Sample.Count   <-  sum(surveycam$Otolith.Sample.Count)
   surveycam.Weight.Sample.Count    <-  sum(surveycam$Weight.Sample.Count)  
   surveycam.Sample.Count           <-  sum(surveycam$Sample_count)  
   
   addition.cam                     <-  c("Movement", "", surveycam.Total.Count, "", 0, 
                                           surveycam.Recovered.Dead.Number, 
                                           0, surveycam.Fork.Len.Tag.Sample.Count, "", surveycam.Fork.Len.Sample.Count,
                                           surveycam.Sex.Sample.Count, surveycam.Maturity.Sample.Count, 
                                           surveycam.Otolith.Sample.Count,
                                           surveycam.Weight.Sample.Count, surveycam.Sample.Count, "", "", "")
   addition.cam  <- prettyNum(addition.cam, big.mark = ",", scientific = FALSE)
   
   # other sets
   surveyspec.other  <-  surveyspec[c(-7,-14,-27,-63),]   # delete camera sets for other and the last line
   
   surveyspec.other.Total.Count            <-  sum(surveyspec.other$Total.Count)
   surveyspec.other.Recovered.Number       <-  sum(surveyspec.other$Recovered.Number)
   surveyspec.other.Recovered.Dead.Number  <-  sum(surveyspec.other$Recovered.Dead.Number)
   surveyspec.other.Released               <-  sum(surveyspec.other$Released)
   surveyspec.other.Fork.Len.Tag.Sample.Count<-  sum(surveyspec.other$Fork.Len.Tag.Sample.Count)
   surveyspec.other.Fork.Len.Sample.Count  <-  sum(surveyspec.other$Fork.Len.Sample.Count)
   surveyspec.other.Sex.Sample.Count       <-  sum(surveyspec.other$Sex.Sample.Count)
   surveyspec.other.Maturity.Sample.Count  <-  sum(surveyspec.other$Maturity.Sample.Count) 
   surveyspec.other.Otolith.Sample.Count   <-  sum(surveyspec.other$Otolith.Sample.Count)
   surveyspec.other.Weight.Sample.Count    <-  sum(surveyspec.other$Weight.Sample.Count)  
   surveyspec.other.Sample.Count           <-  sum(surveyspec.other$Sample_count) 
   
   addition.line.other    <-  c("Other", "", surveyspec.other.Total.Count, "", 
                                surveyspec.other.Recovered.Number, surveyspec.other.Recovered.Dead.Number, 
                                surveyspec.other.Released, surveyspec.other.Fork.Len.Tag.Sample.Count,"", 
                                surveyspec.other.Fork.Len.Sample.Count,
                                surveyspec.other.Sex.Sample.Count, 
                                surveyspec.other.Maturity.Sample.Count, 
                                surveyspec.other.Otolith.Sample.Count,
                                surveyspec.other.Weight.Sample.Count, 
                                surveyspec.other.Sample.Count, "", "", "")
   addition.line.other    <- prettyNum(addition.line.other, big.mark = ",", scientific = FALSE)
   
   # Total
   surveyspec.Total.Count            <-  sum(surveyspec$Total.Count)
   surveyspec.Recovered.Number       <-  sum(surveyspec$Recovered.Number)
   surveyspec.Recovered.Dead.Number  <-  sum(surveyspec$Recovered.Dead.Number)
   surveyspec.Released               <-  sum(surveyspec$Released)
   surveyspec.Fork.Len.Tag.Sample.Count <-  sum(surveyspec$Fork.Len.Tag.Sample.Count)
   surveyspec.Fork.Len.Sample.Count  <-  sum(surveyspec$Fork.Len.Sample.Count)
   surveyspec.Sex.Sample.Count       <-  sum(surveyspec$Sex.Sample.Count)
   surveyspec.Maturity.Sample.Count  <-  sum(surveyspec$Maturity.Sample.Count) 
   surveyspec[is.na(surveyspec)]     <-  0
   surveyspec.Otolith.Sample.Count   <-  sum(surveyspec$Otolith.Sample.Count)
   surveyspec.Weight.Sample.Count    <-  sum(surveyspec$Weight.Sample.Count)  
   surveyspec.Sample.Count           <-  sum(surveyspec$Sample_count) 
   addition.All.Total     <-  c("Total", "", surveyspec.Total.Count, "", 
                                 surveyspec.Recovered.Number, surveyspec.Recovered.Dead.Number, 
                                 surveyspec.Released,  surveyspec.Fork.Len.Tag.Sample.Count,"",
                                 surveyspec.Fork.Len.Sample.Count, surveyspec.Sex.Sample.Count,  
                                 surveyspec.Maturity.Sample.Count, 
                                 surveyspec.Otolith.Sample.Count,
                                 surveyspec.Weight.Sample.Count, 
                                 surveyspec.Sample.Count , "", "", "")
   addition.All.Total     <- prettyNum(addition.All.Total, big.mark = ",", scientific = FALSE)
  
   surveyspec  <- surveyspec %>%
                  mutate(Sparkline = 
                         paste0("\\raisebox{.12\\height} {\\includegraphics[width=2cm]{",path,"fig",SET,".png}}") ) 
   surveyspec  <- surveyspec[, c(1, 2, 3, 18, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17)]  #reorder table
   
   surveyspec  <- surveyspec %>%
                  mutate(Sparkline2 = 
                         paste0("\\raisebox{-.28\\height} {\\includegraphics[width=0.8cm]{",path,"sets_",SET,".png}}") ) 
   
   surveyspec  <- surveyspec[, c(19, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18)]  #reorder table
   
   addition.cam[addition.cam=="      NA"] <- "" 
   addition.line.other[addition.line.other=="    NA"] <- ""
   addition.All.Total[addition.All.Total=="    NA"] <- ""
   surveyspec.Final  <-  rbind(surveyspec,addition.cam,addition.line.other,addition.All.Total)
   
   #tail(surveyspec.Final,3)

   
   colnames(surveyspec.Final) <- c("", "kg","Count","Count by Trap","Recover-Rerelease", "Tag Sample", "Released", 
                                   "Count", "Mean", "Fork Length", "Sex","Maturity", "Otoliths",
                                   "Weight","Count","Proportion Males", "Males", "Females" )
   

   kableExtra::kable(surveyspec.Final,
                     booktabs = TRUE,     
                     longtable = T,
                     escape = F,        # lets the image show up 
                     linesep   = "",
                     align=rep('r', 18),
                     row.names = FALSE,   # in order to get rid of matrix counter
                     format = "latex") %>%
      
   add_header_above(c("Set"= 1,
                      "Total Catch" = 3, 
                      "Tagged Fish Counts" = 3,  
                      "Tagged Fork Lengths(mm)" = 2,
                      "Specimen Count"= 6, 
                      "Mean Fork Length(mm)" = 3), bold = TRUE) %>%
      
   kableExtra::kable_styling(font_size = 8, 
                             latex_options = "repeat_header",
                             repeat_header_text = "continued.", 
                             repeat_header_method = "replace") %>%     
   
   kableExtra::landscape()  %>%
   row_spec(0, bold = T)    %>%   
   column_spec(1,width    = "0.3cm") %>%  # set
   column_spec(2,width    = "0.6cm") %>%  # kg
   column_spec(3,width    = "0.7cm") %>%  # count
   column_spec(4,width    = "1.4cm") %>%  # sparkline      
   column_spec(5,width    = "0.9cm") %>%  # rr
   column_spec(6,width    = "1.3cm") %>%  # tag sample
   column_spec(7,width    = "0.9cm") %>%  # rel     
   column_spec(8,width    = "1.5cm") %>%  # count
   column_spec(9,width    = "0.9cm") %>%  # mean
   column_spec(10,width   = "0.7cm") %>%  # fl
   column_spec(11,width   = "0.6cm") %>%  # sex
   column_spec(12,width   = "0.7cm") %>%  # mat
   column_spec(13,width   = "0.8cm") %>%  # oto 
   column_spec(14,width   = "0.6cm") %>%  # wt
   column_spec(15,width   = "0.6cm") %>%  # cnt
   column_spec(16,width   = "1.1cm") %>%  # prop m
   column_spec(17,width   = "0.7cm") %>%  # male         
   column_spec(18,width   = "0.7cm") %>%  # fem
   row_spec(length(surveyspec.Final$Count) -1, hline_after = T)  %>%  
   row_spec(length(surveyspec.Final$Count) -3, hline_after = T)  %>%
   row_spec(length(surveyspec.Final$Count), bold = T)  
   
```
\clearpage

# SUMMARY OF BIOLOGICAL DATA FOR THE ROUGHEYE/BLACKSPOTTED ROCKFISH COMPLEX. {#app:fifth-appendix} 
Biological data collected for Rougheye/Blackspotted Rockfish complex.  Each set is listed with counts of specimens sampled, calculations of mean fork lengths and the number of species visually identified as either a RE = Rougheye Rockfish, BS = Blackspotted Rockfish or a hybrid. All were captured on StRS sets.
\ \
\ \

```{r appendixE, echo=FALSE}
 
   othersamplesre <-  paste( 
                      "select species_name, [SET], [Len Sample Count], ",
                      "[weight_count], [Sex Sample Count], ",
                      "[Maturity Sample Count], [Otolith Sample Count], [DNA Sample Count], ",
                      "Sample_count, [Proportion Males],  ",   
                      "round([Male Mean Fork Len(mm)],0) as malelen, ",
                      "round([Female Mean Fork Len(mm)],0) as femlen,  ", 
                      "round([NoSexMeanLen(mm)],0) as nosexlen, ", 
                      "bsre.Rougheye, bsre.Blackspotted, bsre.Hybrid ",
                      "from  ",
                      "(select year, TRIP_ID, FE_MAJOR_LEVEL_ID, SPECIES_CODE, ",
                           "SUM(re) AS Rougheye, SUM(bs) AS Blackspotted, SUM(hyb) AS Hybrid ",
                           "from  (select year, TRIP_ID, FE_MAJOR_LEVEL_ID, SPECIES_CODE, ",
                           "CASE WHEN EXISTENCE_ATTRIBUTE_CODE = 16 THEN 1 ELSE 0 END AS re, ",
                           "CASE WHEN EXISTENCE_ATTRIBUTE_CODE = 17 THEN 1 ELSE 0 END AS bs, ",
                           "CASE WHEN EXISTENCE_ATTRIBUTE_CODE = 31 THEN 1 ELSE 0 END AS hyb, ",
                           "SPECIMEN_ID ",
                           "from dbo.gfbio_species_guess) AS bs ",
                           "group by year, TRIP_ID, FE_MAJOR_LEVEL_ID, SPECIES_CODE) AS bsre ", 
                           "RIGHT OUTER JOIN ",
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH ON bsre.TRIP_ID = ",              
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.TRIP_ID and ",
                           "bsre.FE_MAJOR_LEVEL_ID = dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.[SET] ",
                           "and bsre.SPECIES_CODE = ",                       
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.species ",            
                           "where (dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.Year = ", yr, 
                           ") and (dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH.species = N'394') ",
                           "order by species,[SET]", sep="")
   #otherspecre      <-  GetSQLData(othersamplesre,"Sablefish")   # read from SQL Server
   #write.table(otherspecre, file = paste(path,'appendixE.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")   
   otherspecre       <-  read.csv(paste(path,'appendixE.csv',sep=''),header=T) # read from csv
   otherspecre[2,14] <- 0
   otherspecre[2,15] <- 0
   otherspecre[2,16] <- 0
   otherspecre$'Rougheye'     <- as.integer(otherspecre$'Rougheye')
   otherspecre$'Blackspotted' <- as.integer(otherspecre$'Blackspotted')
   otherspecre$'Hybrid'       <- as.integer(otherspecre$'Hybrid')    

   additionre               <-  c('Total','', 
                                 sum(otherspecre$Len.Sample.Count),    sum(otherspecre$weight_count), 
                                 sum(otherspecre$Sex.Sample.Count),    sum(otherspecre$Maturity.Sample.Count),   
                                 sum(otherspecre$Otolith.Sample.Count),sum(otherspecre$DNA.Sample.Count),
                                 sum(otherspecre$Sample_count),'','','','', sum(otherspecre$'Rougheye'),
                                 sum(otherspecre$'Blackspotted'), sum(otherspecre$'Hybrid'))
   otherspecre             <-    rbind(otherspecre,additionre)
   row.countre             <-    length(otherspecre$Set)
   otherspecre             <-    otherspecre[-1]

   
   colnames(otherspecre)   <-  c("Set", "Fork Length",
                               "Weight", "Sex", "Maturity", "Otolith", 
                               "DNA", "Total Count", 
                               "Proportion Males", 
                               "Males", "Females",  
                               "No sex", "RE", "BS","Hybrid" )
   
   addLine <- length(otherspecre$Set)-1
   kableExtra::kable(otherspecre,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     align=c('l','l','l','l','l','l','l','l','l','l','l','l','l','l','l'),
                     format = "latex") %>%
      
   add_header_above(c(" "= 1,
                      "Specimen Count"= 7, 
                      "Mean Fork Length(mm)" = 4,
                      "Sampler Visual id" = 3), bold=TRUE) %>%
   
   kableExtra::kable_styling(font_size = 8, 
                        latex_options = "repeat_header",
                        repeat_header_text = "continued.", 
                        repeat_header_method = "replace") %>%
      
   #kableExtra::landscape()  %>% 
         
      column_spec(1,width     = "0.5cm") %>% # set
      column_spec(2,width     = "0.7cm") %>% # fl 
      column_spec(3,width     = "0.7cm") %>% # wt   
      column_spec(4,width     = "0.4cm") %>% # sex 
      column_spec(5,width     = "0.7cm") %>% # mat
      column_spec(6,width     = "0.6cm") %>% # oto
      column_spec(7,width     = "0.5cm") %>% # dna
      column_spec(8,width     = "0.5cm") %>% # cnt        
      column_spec(9,width     = "1.0cm") %>% # prop m
      column_spec(10,width    = "0.7cm") %>% # male
      column_spec(11,width    = "0.8cm") %>% # female
      column_spec(12,width    = "0.5cm") %>% # no sex  
      column_spec(13,width    = "0.4cm") %>% # re
      column_spec(14,width    = "0.4cm") %>% # bc
      column_spec(15,width    = "0.4cm") %>% # hybrid 
      row_spec(0, bold = T) %>%
      row_spec(addLine,  hline_after = T) %>%
      row_spec(row.countre, bold = T)

```
\clearpage

# SUMMARY OF BIOLOGICAL DATA FOR OTHER ROCKFISH SPECIES. {#app:sixth-appendix} 
Biological data collected for other rockfish species.  Each set is listed with counts of specimens sampled and calculations of mean fork lengths.  All were captured on StRS sets.

\ \

```{r appendixF, echo=FALSE}
 
   othersamples <-  paste( "SELECT species_name, [SET], [Len Sample Count], ",
                           "weight_count, [Sex Sample Count], [Maturity Sample Count], ",
                           "[Otolith Sample Count], [DNA Sample Count], Sample_count,  ",
                           "[Proportion Males], ROUND([Male Mean Fork Len(mm)], 0) AS malelen,  ",
                           "ROUND([Female Mean Fork Len(mm)], 0) AS femlen,  ",
                           "ROUND([NoSexMeanLen(mm)], 0) AS nosexlen  FROM  ",                                    
                           "dbo.GFBIO_RESEARCH_SAMPLE_DETAILS_OTHER_FISH ", 
                           "WHERE (Year = ",yr,") AND (species <> N'394') ", 
                           "ORDER BY species, [SET]  ", sep="")
   #otherspec2            <-  GetSQLData(othersamples,"Sablefish")   # read from SQL Server
   #write.table(otherspec2, file = paste(path,'appendixF.csv',sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",")   
   otherspec2              <-  read.csv(paste(path,'appendixF.csv',sep=''),header=T) # read from csv
   otherspec2$species_name <-  as.character(otherspec2$species_name)

   otherspec2$species_name<-  cleanf(otherspec2$species_name)
   #otherspec2             <-  otherspec2[c(-8)]
   colnames(otherspec2)   <-  c("Species Name", "Set", "Fork Length",
                               "Weight", "Sex","Maturity", "Otoliths", "DNA",
                               "Total", 
                               "Prop Males", 
                               "Males", "Females",  
                               "No sex" )
   
      kableExtra::kable(otherspec2,
                     booktabs = TRUE, 
                     longtable = T,
                     linesep   = "",
                     align=c('l','l','l','l','l','l','l','l','l','l','l','l','l'),
                     format = "latex") %>%
      
      add_header_above(c(" "= 2,
                         "Specimen Count"= 7, 
                         "Mean Fork Length(mm)" = 4), bold=TRUE) %>%
   
      kableExtra::kable_styling(font_size = 8, 
                       latex_options = "repeat_header",
                       repeat_header_text = "continued.", 
                       repeat_header_method = "replace") %>%

      column_spec(1,width     = "3.5cm") %>% # species
      column_spec(2,width     = "0.5cm") %>% # set
      column_spec(3,width     = "0.7cm") %>% # fl 
      column_spec(4,width     = "0.7cm") %>% # wt   
      column_spec(5,width     = "0.4cm") %>% # sex 
      column_spec(6,width     = "0.7cm") %>% # mat
      column_spec(7,width     = "0.7cm") %>% # oto
      column_spec(8,width     = "0.7cm") %>% # dna 
      column_spec(9,width     = "0.2cm") %>% # tot cnt        
      column_spec(10,width     = "1.0cm") %>% # prop m
      column_spec(11,width    = "0.5cm") %>% # male
      column_spec(12,width    = "0.7cm") %>% # female
      column_spec(13,width    = "0.6cm") %>% #  no sex  
      row_spec(0, bold = T) %>%
      row_spec(16,  hline_after = T)
```

<!-- At the end of your appendices add: -->
`r if(knitr:::is_latex_output()) '% end csasdown appendix'`
